GA3

### 2022-08-19 graphs_newt_snakes/GA3.Rmd
working on writing about the file results. Finding problems with some of them

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){

  pattern="1.0e-08_0.005_1.0e-10_0.05_2"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

@@

  if(nrow(cfile)>nrow(file)){
    toDelete <- seq(0, nrow(cfile), 2)
    cfile_short <-  cfile[-toDelete, ]
  }else{
    cfile_short <-  cfile
  }
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

@@

```{r, GA3 cor and pheno}
GA3_pattern <- unique(paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep))

@@

```{r, cor grid by location}

@@

```{r, cor grid by location}

@@

```{r, cor grid by location}

@@

```{r, cor grid by location}

spegen=1001
#spegen=30001
#unique(GA3_grid_tall_file$snake_newt_rep)
GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
GA3<-GA3[1,]
GA3_ind = GA3[,grepl("generation|num_ind", names(GA3)) ]

@@

```{r, cor grid by location}

>>>>

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=GA3_tall_tall_file
#cfile=GA3_cor_tall_file 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

@@

  if(nrow(cfile)>nrow(file)){
    toDelete <- seq(0, nrow(cfile), 2)
    cfile_short <-  cfile[-toDelete, ]
  }else{
    cfile_short <-  cfile
  }

  if(nrow(cfile_short)>nrow(file)){
      toDelete <- seq(0, nrow(cfile_short), 2)
      cfile_short <-  cfile_short[-toDelete, ]
    }
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

@@

```{r, GA3 cor and pheno, results="hide"}
GA3_pattern <- unique(paste0(GA3_tall_tall_file$snake_mu_rate, "_", GA3_tall_tall_file$snake_mu_effect_sd,"_",GA3_tall_tall_file$newt_mu_rate, "_", GA3_tall_tall_file$newt_mu_effect_sd, "_", GA3_tall_tall_file$rep))

@@

```{r, cor grid by location 1}

@@

```{r, cor grid by location 2}

@@

```{r, cor grid by location 3}

@@

```{r, cor grid by location 4}

#GA3_grid_tall_file
file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_0"
#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0

spegen=15001
#unique(GA3_grid_tall_file$snake_newt_rep)
GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
GA3<-GA3[1,]
GA3_mean = GA3[,grepl("generation|mean", names(GA3)) ]

#spegen=30001
#unique(GA3_grid_tall_file$snake_newt_rep)
GA3<-GA3_GA3_grid_tall_file[which(GA3_GA3_grid_tall_file$snake_newt_rep==file_name & GA3_GA3_grid_tall_file$generation==spegen),]
GA3<-GA3[1,]
GA3_ind = GA3[,grepl("generation|num_ind", names(GA3)) ]

@@

```{r, cor grid by location 5}
